\documentclass{beamer}

\usetheme{Madrid} % Clean theme; alternatives: "metropolis", "Boadilla", "CambridgeUS"
\usecolortheme{seahorse}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}

\title[Project Pitch: \textit{Sarajevo Apartment Price prediction}] % Short title for sidebar
{Project Pitch: \textit{Sarajevo Apartment Price prediction}}
\author[Emre, Mustafa]{Emre Arapčić-Uevak \and Mustafa Sinanovic}
\date{\today}
\institute[IUS]{
  International University of Sarajevo \\
  Faculty of Engineering and Natural Sciences
}

\begin{document}

% Title Slide
\frame{\titlepage}

\begin{frame}{What will be covered?}
  \tableofcontents
\end{frame}

\AtBeginSection[]
{
  \begin{frame}{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}

\section{Introduction \& Problem Statement}

\subsection{What is the real-world problem?}
\begin{frame}{What is the real-world problem?}
  \only<1>{
    In the modern housing market, both \textbf{apartment sale prices} and \textbf{rental prices} can vary drastically depending 
    on factors such as location, size, number of rooms, building condition, and surrounding amenities. \newline 
  }
  
  \only<2>{
    However, in many listings, especially on local platforms, price information is often missing, incomplete, or inconsistent.
    This makes it difficult for potential buyers, tenants, and even property owners to assess the true value of an apartment or to set a fair and competitive price.
  }
\end{frame}

\subsection{Why is it important or relevant?}
\begin{frame}{Why is it important or relevant?}
  \only<1>{
    For most people, housing is the \alert{largest financial decision} they will make, yet reliable pricing information is often 
    unavailable. \newline 

    When price data is missing or unrealistic, users have no objective way to determine whether a listing is underpriced, 
    overpriced, or fair. 
  }

  \only<2>{
    A system capable of accurately predicting housing and rental prices would:
    \begin{itemize}
      \item[$\bullet$] Help buyers and renters make more informed decisions.
      \item[$\bullet$] Allow property owners to estimate realistic values for their listings.
      \item[$\bullet$] Enable market analysis, regional comparisons, and price trend visualizations for researchers or real estate agencies.
    \end{itemize}
  }
\end{frame}

\subsection{Our Goal}
\begin{frame}{Our Goal}
  Our goal is to build a predictive model that can estimate both apartment sale prices and rental prices based on publicly 
  \emph{available data}, and integrate the model into an application for ease of use. \pause
  
  \vspace{0.5cm}
  Some concrete examples:
  \begin{enumerate}    
    \item<2-> Interactive map
    \item<3-> Price Fairness Indicator
    \item<4-> Price Prediction Tool for Listings
  \end{enumerate}
\end{frame}

\end{document}